---
title: "hw5"
author: "tianwei zhao"
date: "11/19/2021"
output: github_document
---

```{r}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

```{r}
homicides_df = 
  read_csv("./data/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved")
    ) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

#### Describe the data

This dataset consists of 52178 observations and 14 variables a tidying it up. Each row of the data is a reported homicide case, including record of the victim’s name, race/ethnicity, age, sex, location of the crime, and whether the crime was solved.


#### Resolution of each City
```{r}
homicides_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()) 
```

#### Baltimore
```{r}
baltimore_df = 
  homicides_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n())

balimtore_test = 
  prop.test(x = baltimore_summary %>% pull(unsolved), 
            n = baltimore_summary %>% pull(n))

balimtore_test %>% 
  broom::tidy()
```

####For all Cities

Function
```{r}
prop_test_function = function(city_df) {
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test = 
    prop.test(x = city_summary %>% pull(unsolved), 
            n = city_summary %>% pull(n))
  
  return(city_test)
}
```

Use the function and iterate across all cities

```{r}
results_df = 
  homicides_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

results_df
```


#### plot

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2, hjust = 1))
```

## Problem 2

Tidy the Dataframe

```{r}
arm_df = 
  #dataframe containing all file names
  tibble(
    file_name = list.files("data/pro2/data/")) %>% 
  #Iterate over file names and read in data for each subject using map and saving the result as a new variable in the dataframe
  mutate(
    subject_data = map(str_c("data/pro2/data/",file_name), read_csv)) %>% 
  #unnest the data for each subject
  unnest(subject_data)

#tidy the dataset 
subject_df = 
  arm_df %>% 
    #manipulate file names to include control arm and subject ID
    separate(file_name, into = c("arm", "id"), sep = "_") %>% 
    #tidy the variable names
    mutate(
      id = str_replace(id,".csv","")
    ) %>% 
  #tidy data for each week
    pivot_longer(
      week_1:week_8,
      names_to = "week",
      names_prefix = "week_",
      values_to = "observation"
    ) %>% 
  #assign appropriate classes to the variables
  mutate(
    arm = recode(arm, con = "control", exp = "experimental"),
    arm = factor(arm),
    id = factor(id),
    week = as.integer(week)
  )

subject_df
```

Spaghetti plot

```{r}
subject_df %>% 
  ggplot(aes(x = week, y = observation, group = id, color = id)) +
  geom_point() +
  geom_line() +
  facet_grid(. ~ arm)
```

From the plots, we can observe that the observed data has no significant variation through the 8 weeks period for the control group. However, for the experimental group, there exists a positive trend for the observation value, indicating that there is a positive linear relationship.


## Problem 3

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

```{r}
fill_na = function(vec){
  
  if (is.numeric(vec)) {
    replace_na(vec, round(mean(vec, na.rm = TRUE),digits = 2))
  }
  
  else if (is.character(vec)) {
    replace_na(vec, "virginica")
  }
}
```



Use the map function to apply each element in the iris_with_missing dataframe to the fill_na function above. More specifically, use the map_dfr function to return a dataframe created by row-binding.

```{r}
map_dfr(iris_with_missing, fill_na)
```

